#make balanced dataset for Ua model

 ##210115
 
#load dataset and filtering
```{r}
library(dplyr)

df_ori <- read.csv("~/KNHANES_eGFR/eGFR_urine.v2.csv", fileEncoding = "utf-8")

df_sub <- df_ori %>%
  filter(age>=18)

glimpse(df_sub)
```

#check statistical 
```{r}
library(knitr)
library(MatchIt)
library(pacman)
library(labelled)
library(optmatch)
set.seed(0)
pacman::p_load(tableone)

name_list <- colnames(df_sub)[6:16]
name_list

df_ua <- CreateTableOne(vars = c(name_list), 
                        data = df_sub, 
                        factorVars = c(name_list[c(1,4)]), 
                        strata = "eGFR_ab") %>% 
  print()

kable(df_ua, align = 'c', caption = "base table")
```
#psm
```{r}
psm <- matchit(eGFR_ab ~ age + male, data = df_sub, method = "nearest")
```

#result of psm
```{r}
summary(psm)
plot(psm, type = "jitter", interactive = F)
```

#result table of psm
```{r}
df_psm <- match.data(psm)

t_2 <- CreateTableOne(vars = c(name_list),
                     data = df_psm,
                     factorVars = c(name_list[c(1,4)]),
                     strata = "eGFR_ab") %>%
  print()

kable(t_2, align = "c")
```

#save as write.csv
```{r}
#write.csv(df_psm, "~/KNHANES_eGFR/eGFR_urine_psm.v1.csv", row.names = F, fileEncoding = "utf-8")
```

#finding ratio of p-val <0.05

#age p-val deadline : ratio=3
```{r}
psm_r3 <- matchit(eGFR_ab ~ age + male, data = df_sub, method = "nearest", ratio=3)

#dataframe matched data
df_psm_r3 <- match.data(psm_r3)

#table matched data
r3 <- CreateTableOne(vars = c(name_list),
                     data = df_psm_r3,
                     factorVars = c(name_list[c(1,4)]),
                     strata = "eGFR_ab") %>%
  print()

kable(r3, align = "c")

#save as csv
#write.csv(df_psm_r3, "~/KNHANES_eGFR/eGFR_urine_psm.v2.csv", row.names = F, fileEncoding = "utf-8")
```

# age p-val <0.05 : ratio=4
```{r}
psm_r4 <- matchit(eGFR_ab ~ age + male, data = df_sub, method = "nearest", ratio=4)

#dataframe matched data
df_psm_r4 <- match.data(psm_r4)

#table matched data
r4 <- CreateTableOne(vars = c(name_list),
                     data = df_psm_r4,
                     factorVars = c(name_list[c(1,4)]),
                     strata = "eGFR_ab") %>%
  print()

kable(r4, align = "c")

#save as csv
#write.csv(df_psm_r4, "~/KNHANES_eGFR/eGFR_urine_psm.v3.csv", row.names = F, fileEncoding = "utf-8")
```