---
title: "Summary knhanes 12y dataset sort by age"
output: html_notebook
---
#summary table 60model
```{r}
#https://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
library(arsenal)

df <-read.csv("~/proj_ua/data/knhanes_12y_age.v1.csv", fileEncoding = 'utf-8')
glimpse(df)

df_summary <- df %>%
  mutate(
    male = as.character(male),
    eGFR_ab = as.character(eGFR_ab),
    he_unitr= as.character(he_unitr),
    he_upro = as.character(he_upro),
    he_uglu = as.character(he_uglu),
    he_uket = as.character(he_uket),
    he_ubil = as.character(he_ubil),
    he_ubld = as.character(he_ubld),
    he_uro = as.character(he_uro),
  ) %>%
  select(-c(id, id_fam, psu, kstrata, wt_12y)) %>%
  filter(age>=20)

df_summary <- df_summary[,c(4,3,1,2,5:14)]
glimpse(df_summary)

stat_tbl <- tableby(level~ . ,data=df_summary)
summary(stat_tbl)
kable(summary(stat_tbl))
```
#summary table // kmeans 
```{r}
#https://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
library(arsenal)

df2 <-read.csv("~/proj_ua/data/knhanes_12y_kmeans.v1.csv", fileEncoding = 'utf-8')
glimpse(df2)

df2_summary <- df2 %>%
  mutate(
    male = as.character(male),
    eGFR_ab = as.character(eGFR_ab),
    he_unitr= as.character(he_unitr),
    he_upro = as.character(he_upro),
    he_uglu = as.character(he_uglu),
    he_uket = as.character(he_uket),
    he_ubil = as.character(he_ubil),
    he_ubld = as.character(he_ubld),
    he_uro = as.character(he_uro),
  ) %>%
  select(-c(id, id_fam, psu, kstrata, wt_12y)) %>%
  filter(age>=20)
glimpse(df2_summary)

df2_summary2 <- df2_summary[,c(4,3,1,2,5:14)]
glimpse(df2_summary2)

df2_summary3 <- df2_summary[,c(4,3,1,2,5:13,15)]
glimpse(df2_summary3)

stat_tbl2 <- tableby(level~ . ,data=df2_summary2)
summary(stat_tbl2)
kable(summary(stat_tbl2))

stat_tbl3 <- tableby(level2~ . ,data=df2_summary3)
summary(stat_tbl3)
kable(summary(stat_tbl3))
```

#summary table 45model
```{r}
#https://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
library(arsenal)

df <-read.csv("~/proj_ua/data/knhanes_12y_age.v2.csv", fileEncoding = 'utf-8')
glimpse(df)

df_summary <- df %>%
  mutate(
    male = as.character(male),
    eGFR_ab45 = as.character(eGFR_ab45),
    he_unitr= as.character(he_unitr),
    he_upro = as.character(he_upro),
    he_uglu = as.character(he_uglu),
    he_uket = as.character(he_uket),
    he_ubil = as.character(he_ubil),
    he_ubld = as.character(he_ubld),
    he_uro = as.character(he_uro),
  ) %>%
  select(-c(id, id_fam, psu, kstrata, wt_12y)) %>%
  filter(age>=20)
glimpse(df_summary)
df_summary <- df_summary[,c(4,3,1,14,5:13,15)]
glimpse(df_summary)

stat_tbl <- tableby(level~ . ,data=df_summary)
summary(stat_tbl)
kable(summary(stat_tbl))
```
#summary table 60model / proteinuria in positive cases
```{r}
#https://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
library(arsenal)

df <-read.csv("~/proj_ua/data/knhanes_12y_age.v1.csv", fileEncoding = 'utf-8')
glimpse(df)

df_summary <- df %>%
  mutate(
    male = as.character(male),
    eGFR_ab = as.character(eGFR_ab),
    he_unitr= as.character(he_unitr),
    he_upro = as.character(he_upro),
    he_uglu = as.character(he_uglu),
    he_uket = as.character(he_uket),
    he_ubil = as.character(he_ubil),
    he_ubld = as.character(he_ubld),
    he_uro = as.character(he_uro),
  ) %>%
  select(-c(id, id_fam, psu, kstrata, wt_12y)) %>%
  filter(age>=20, eGFR_ab==1)

glimpse(df_summary)
df_summary <- df_summary[,c(4,3,1,2,5:13,15)]
glimpse(df_summary)

stat_tbl <- tableby(level~ . ,data=df_summary)
summary(stat_tbl)
kable(summary(stat_tbl))
```

#summary table 60model / age<80
```{r}
#https://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
library(arsenal)

df <-read.csv("~/proj_ua/data/knhanes_12y_age.v1.csv", fileEncoding = 'utf-8')
glimpse(df)

df_summary <- df %>%
  mutate(
    male = as.character(male),
    eGFR_ab = as.character(eGFR_ab),
    he_unitr= as.character(he_unitr),
    he_upro = as.character(he_upro),
    he_uglu = as.character(he_uglu),
    he_uket = as.character(he_uket),
    he_ubil = as.character(he_ubil),
    he_ubld = as.character(he_ubld),
    he_uro = as.character(he_uro),
    level = ifelse(age<68, 0, ifelse(age<=74, 1, 2))
  ) %>%
  select(-c(id, id_fam, psu, kstrata, wt_12y)) %>%
  filter(age>=20, age<80)

glimpse(df_summary)
df_summary <- df_summary[,c(4,3,1,2,5:14)]
glimpse(df_summary)

stat_tbl <- tableby(level~ . ,data=df_summary)
summary(stat_tbl)
kable(summary(stat_tbl))
```

#summary table 60model / age<80 kmeans
```{r}
#https://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
library(arsenal)

df <-read.csv("~/proj_ua/data/knhanes_12y_age.v1.csv", fileEncoding = 'utf-8')
glimpse(df)

df_summary <- df %>%
  mutate(
    male = as.character(male),
    eGFR_ab = as.character(eGFR_ab),
    he_unitr= as.character(he_unitr),
    he_upro = as.character(he_upro),
    he_uglu = as.character(he_uglu),
    he_uket = as.character(he_uket),
    he_ubil = as.character(he_ubil),
    he_ubld = as.character(he_ubld),
    he_uro = as.character(he_uro),
    level = ifelse(age<56, 0, ifelse(age<69, 1, 2))
  ) %>%
  select(-c(id, id_fam, psu, kstrata, wt_12y)) %>%
  filter(age>=20, age<80)

glimpse(df_summary)
df_summary <- df_summary[,c(4,3,1,2,5:14)]
glimpse(df_summary)

stat_tbl <- tableby(level~ . ,data=df_summary)
summary(stat_tbl)
kable(summary(stat_tbl))
```